Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
fixed verbatim removed appendix

The supplementary materials include the maize experiment data ({\tt data.csv}), a script to run our method ({\tt script.R}), and {\tt Stan} models: all genes independent (\verb@\tt model_ind.txt\verb@) and covariance (\verb@model_cov.txt\verb@) models used in obtaining MAP estimates and single gene independent (\verb@\tt sg_model_ind.txt\verb@) and covariance (\verb@sg_model_cov.txt\verb@) models used in performing the MCMC on single genes.

@@

\appendix

%  To get the journal style of heading for an appendix, mimic the following.

\section{}

>>>>

The supplementary materials include the maize experiment data ({\tt data.csv}), a script to run our method ({\tt script.R}), and {\tt Stan} models: all genes independent (\verb@model_ind.txt@) and covariance (\verb@model_cov.txt@) models used in obtaining MAP estimates and single gene independent (\verb@sg_model_ind.txt@) and covariance (\verb@sg_model_cov.txt@) models used in performing the MCMC on single genes.

@@

% \appendix
% %  To get the journal style of heading for an appendix, mimic the following.
% \section{}
% \subsection{Material here}
